---
title: "Simulate a binomial response and random effects"
author: "Eamonn O'Brien"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document:
    toc: true
    toc_depth: 2
  fig_height: 6
  fig_width: 8
header-includes:
- \usepackage{eso-pic,graphicx,transparent}
- \usepackage{graphicx}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \setlength\headheight{22pt}
- \fancyfoot[RO]{Simulation}
- \usepackage{lastpage}
- \cfoot{Page \thepage\ of \pageref{LastPage}}
---

\newpage  
\tableofcontents  
\listoffigures
\listoftables
\newpage

```{r set-options, echo=FALSE, cache=FALSE, warning = FALSE}

         set.seed(123)
         startTime<-proc.time()
         library(knitr)
         options(width=60)

         opts_chunk$set(comment = "", warning = FALSE, message = FALSE,
                       echo = TRUE, tidy = TRUE, size="tiny",  cache=TRUE,
                       progress=TRUE, tidy.opts=list(width.cutoff=60),
                         fig.width=7, fig.height=3.5,
                       cache.path = 'program_Cache/',
                       fig.path='figure/')
         
        # opts_chunk$set(tidy.opts=list(width.cutoff=80),tidy=TRUE) 
         
        knitr::knit_hooks$set(inline = function(x) {
          knitr:::format_sci(x, 'md')
        })
         
        
        options(scipen=999)  # remove scientific notation
        

         # create an R file of the code!
        # https://stackoverflow.com/questions/26048722/knitr-and-tangle-code-without-execution
        
         # knit_hooks$set(purl = function(before, options) {
         #   if (before) return()
         #   input  = current_input()  # filename of input document
         #   output = paste(tools::file_path_sans_ext(input), 'R', sep = '.')
         #   if (knitr:::isFALSE(knitr:::.knitEnv$tangle.start)) {
         #   assign('tangle.start', TRUE, knitr:::.knitEnv)
         #   unlink(output)
         # }
         #   cat(options$code, file = output, sep = '\n', append = TRUE)
         # })

   
     #   list.of.packages <- c("tidyverse")  # haven causes a problem
        
     #   new.packages <- list.of.packages[!(list.of.packages %in% 
     #   installed.packages()[,"Package"])]
     #   if(length(new.packages)) install.packages(new.packages)
     #   sapply(X = list.of.packages, require, character.only = TRUE)
         
         
 
```

## Some functions

```{r ,echo=FALSE}



      wd <- getwd()
      wd.code <- wd #paste0(Rhome,'CODE DEVELOPMENT')                  # note this new dir
      wd.data <- wd # paste0(Rhome,'DATA')
 
    # rounding functions
      p2 <- function(x) {formatC(x, format="f", digits=2)}
      p3 <- function(x) {formatC(x, format="f", digits=3)}
      p4 <- function(x) {formatC(x, format="f", digits=4)}
      
       # function to calculate the mode     
      getmode <- function(v) {
           uniqv <- unique(v)
           uniqv[which.max(tabulate(match(v, uniqv)))]
          }
 
       
        #perhaps help colour plot text based on loop count
      is.even <- function(x){ x %% 2 == 0 }
           
      options(width=90)


```

## Introduction

```{r} 

cat("\nI simulate between country and between site SD with an underlying mean (see reference where code was helpful).\n")

```

## Population parameters  & Design Paramters for simulation

```{r, echo=TRUE}
   

# mu: underlying mean of the outcome in the control group
# beta1: covariate not used
# sdcountry: sd of random effect at the country level (sd for the bi)
# sdsite: sd of random effect at the site level (sd for the bij)

# Design parameters
# countries: number of countries
# sites: number of sites per country
# persons : number of persons per site
     
    mu = 0.8   # 0.5 means odds = 1, so intercept should be zero (log odds)
    (reg.intercept <- log(mu/(1-mu)))  #   the intercept of the regression model should approximate this (odds)
    # get back to prob
    exp( reg.intercept)/(1+ exp(reg.intercept))  # convert log odds to prob
    

    beta1=1    # if this was 1, means no difference, log(1)==0 * trt 

    sdcountry= 0.2 # this is on the log odds scale
    sdsite = 0.4   # this is on the log odds scale

    # Design Parameters
    countries = 25   # no of countries
    
    # no of sites in countries
    sites <- MASS::rnegbin(countries, mu = 10, theta = 1.6)
    sites <- ifelse(sites==0, 1 , sites) # dont want 0s
    
    # no persons at each site
    persons <- MASS::rnegbin(sum(sites), mu = 11, theta = 2) + 1 # dont want any 0s hence the + 1
  
```

## Examine simulation data

```{r, echo=TRUE}
    
    sum(persons) 
    sites                        # shows the number of sites in each of the countries
    sequence(sites)              # expand the sites
    persons                      # shows the persons at each site
    rep(1:length(sites), sites)  # grouping indicator for sites
    
  
```

## Create unbalanced data. Trial and error to program this!

```{r, echo=TRUE}

    # pp <- seq_along(rep(persons, persons))# count of persons (not really needed)
    pp <- rep(1:sum(persons))               # count of persons (not really needed) but simpler
    g <- rep(1:length(persons), persons)    # person in each site is 'flattened' 
    x <- rep(1:length(sites), sites)        # sites ditto
    country <- rep(x, persons)              # countries
    
    # put tx in there for now although it does not vary
    tx=1
    d <- cbind( country=country, site=g, person=pp , tx=tx)  # create a data frame
    summary(d)
    
    #draw random effects for clusters
    countryRE <- rnorm(countries,0,sdcountry)
    siteRE <- rnorm( sum(sites),0,sdsite)
    

    #create outcome
    (prob <- 1/(1 + exp(-( log(mu/(1-mu)) + log(beta1)*tx + countryRE[d[,1]] + siteRE[d[,2]] ))))
    (y <- rbinom(sum(persons), 1, prob))


    # create 
    d <- as.data.frame(cbind(y,d))
    d$country <- as.factor(d$country)
    d$site <- as.factor(d$site)

  
```

## Frequentist random effects model

```{r, echo=TRUE}

    require(lme4)
    fit0 = glmer(
      data = d,
        formula = y ~ (1|country/site),
      family= binomial
    )
    print(fit0)

   # (fit0fci <- confint(fit0))  # takes some time
    
    coef(fit0)
  
    # are these sensible from binomial?
    plot(fit0)
    qqnorm(residuals(fit0))
    hist(residuals(fit0))

    fit0r <- ranef(fit0, condVar = TRUE)   # frequentist estimates of random effects

    coef(fit0)
    ranef(fit0, condVar = TRUE)  


    predFun <- function(fit0) {
        predict(fit0)
    }
    bb <- bootMer(fit0,nsim=200,FUN=predFun,seed=101)
    
    # https://stats.stackexchange.com/questions/147836/prediction-interval-for-lmer-mixed-effects-model-in-r
    c(attr(ranef(fit0,condVar=TRUE)[[1]],"postVar"))  # site variances 
    c(attr(ranef(fit0,condVar=TRUE)[[2]],"postVar"))  # country variances 

```

## Use sandwich approach in reference , although I think it can only handle one cluster

```{r, echo=TRUE}    

    require(rms)
    dd <- datadist(d)   #  Run for all potential vars.
    options(datadist="dd") 
    
    d$tx <- rnorm(sum(persons), 0, 1) # need to do this otherwise intercept model has no covar matrix
    o <- try(lrm(y~1 + tx,x=TRUE,y=TRUE, d))
    (v <- robcov(fit=o,cluster=d[,c(2)]))   # can I cluster on multiple variances - no?

    summary(v)
    
```

## Analysis ignoring clustering

```{r, echo=TRUE}  

    binom::binom.confint(sum(d$y==1), length(d$y))

```

## Bayesian

```{r, echo=TRUE, eval=TRUE}

    require(brms)
    require(rstan)

    rstan_options(auto_write = TRUE)
   # options(mc.cores = parallel::detectCores())

    fit = brm(
        formula = y ~ (1|country/site),
      family= bernoulli, data = d, seed=123,
    )
    print(fit)
    
    f <- fit # selected model, default priors used

    # save the workspace
 #  save.image(file=  "brms bernouli model.RData" )
   
  
```

## Load Bayesian analysis

```{r , eval=TRUE}

  # load(file="brms bernouli model.RData" )  #site sd=2.5, country=0.5
    # library(brms)

```

## Check Model

```{r, echo=TRUE ,eval=TRUE} 


  
  print(f)

  pp_check(f)  # shows dens_overlay plot by default
  pp_check(f, type = "error_hist", nsamples = 11)    # 11 draws
  pp_check(f, type = "scatter_avg", nsamples = 100)  # mean on x axis y observed
  #pp_check(f, type = "stat_2d")  ## took a long time so cancelled this
  #pp_check(f ,x="vas", type = "intervals") ## took a long time so cancelled this
  pp_check(f, type = "scatter", nsamples=2)
  
 # pp_check(f,x="avisit",type = "error_scatter_avg_vs_x", nsamples = 10)  #throwing error
 # pp_check(f,x="vas", type = "ribbon", nsamples = 20) #throwing error
  pp_check(f ,type = "error_scatter", nsamples = 6)

  stanplot(f, type = "hist")
 
```

## Predictions

```{r, echo=TRUE ,eval=TRUE} 


  print(f)

  f1 <- fitted(f,  re_formula=NULL)   # include all random effects
  head(f1)     #site level
  f2 <- fitted(f,  re_formula=NA)     # no random effects
  head(f2)     # intercept only
  
  f3 <- predict(f, re_formula=NULL)   # include all random effects
  head(f3)     #individual
  f4 <- predict(f, re_formula=NA)     # no random effects
  head(f4)     #indivdual
  
  f5 <- predict(f, re_formula = ~ (1|country))
  head(f5)     #not sure
  f6 <- predict(f, re_formula = ~ (1|site))
  head(f6) # individual level
  
  f8 <- fitted(f, re_formula = ~ (1|country))
  head(f8)    #country level
  f9 <- fitted(f, re_formula = ~ (1|country/site))
  head(f9)    #site level only same as f1
  
 
```

## Plot Bayesian site level predictions

```{r, echo=TRUE ,eval=TRUE, fig.width=7, fig.height=12} 


    pred <- f1 # f9
    df <- data.frame(cbind(pred, d))
    df$label <- df$site

 # start here use coefficients from model rather than predictions
    A <- function(x) 1/(1+exp(-x))
 
    e1 <- A(fixef(fit)[,'Estimate'])
    e2 <- A(fixef(fit)[,'Q2.5'])
    e3 <- A(fixef(fit)[,'Q97.5'])

    bc <- coef(fit, old=FALSE, summary=TRUE)$`country:site`
    df <- as.data.frame(bc)
    names(df) <- dimnames(bc)[[2]]
    df$sites <-     gsub(".*_", "", rownames(df))
    df$countries <- gsub("_.*", "", rownames(df))
 
    df <- data.frame(df[,c(2,5,6)], apply(df[,c(1,3,4)],2, A) )
 
    df <- df[,c(3,2,4,1,5,6)]

    df$label <- df$sites
    df$label <- as.numeric(as.character(df$label))
    df <- df[order(df$label),]
    # reverses the factor level ordering for labels after coord_flip()
   # df <- df[order(sites),]
    df$label <- factor(df$label, levels=rev(unique(df$label)), ordered = T)
     
    # df$label <- factor(   df$label, levels=unique(as.character(   df$label)) )

    fp <- NULL
    fp <- ggplot(data=df, aes(x=label, y=Estimate, ymin=Q2.5, ymax=Q97.5, colour=label)) +
      geom_pointrange() +
         geom_hline(yintercept=mu, color="green",lty=2) +  # add a dotted line 
      
      geom_hline(yintercept=e1,  color="blue", linetype="dashed") +  # estimate
      geom_hline(yintercept=e2,   color="blue", linetype="dashed") +   
      geom_hline(yintercept=e3,    color="blue", linetype="dashed") +   
      coord_flip() +  # flip coordinates (puts labels on y axis)
      xlab("Label") + ylab("Mean (95% CI)") +
      theme_bw() + # use a white background
      theme(legend.position="none") +
     ggtitle("Site level predictions") 
    print(fp)
    
```

## Plot Bayesian country level predictions

```{r, echo=TRUE ,eval=TRUE} 
    
    #these are predictions 
    pred <- f8
    df <- data.frame(cbind(pred, d))
    df$label <- df$country

    # start here use coefficients from model rather than predictions
    bc <- coef(fit, old=FALSE, summary=TRUE)$country
    df <- as.data.frame(bc)
    names(df) <- dimnames(bc)[[2]]
    df$label <- unique(d$country)
  

    df <- data.frame(df[,c(2,5)], apply(df[,c(1,3,4)],2, A) )
    df <- df[,c(2,3,1,4,5)]

    # reverses the factor level ordering for labels after coord_flip()
    df$label <- factor(df$label, levels=rev(unique(df$label)), ordered = T)
    
    fp <- NULL
    fp <- ggplot(data=df, aes(x=label, y=Estimate, 
                              ymin=df[,4], ymax=df[,5], colour=label)) +
      geom_pointrange() +
      geom_hline(yintercept=mu, color="green",lty=2) +  # add a dotted line 
      
      geom_hline(yintercept=e1, color="blue", linetype="dashed") +  # estimate
      geom_hline(yintercept=e2,    color="blue", linetype="dashed") +   
      geom_hline(yintercept=e3,    color="blue", linetype="dashed") +   
  
      coord_flip() +  # flip coordinates (puts labels on y axis)
      xlab("Country") + 
      ylab("Mean (95% CI)") +
      theme_bw() + # use a white background
      theme(legend.position="none") +
      ggtitle("Country level predictions") 
    print(fp)


  # fitted_values <- fitted(fit)
  # head(fitted_values)
  # plot fitted means against actual response
  # dat <- as.data.frame(cbind(Y = standata(fit)$Y, fitted_values))
  # ggplot(dat) + geom_point(aes(x = Estimate, y = Y))
  
```

## Exploring

```{r, echo=TRUE ,eval=TRUE}  
  
  newdata <- data.frame(country = 1, site=1, person=1)
  predict(fit, newdata = newdata)
  
  f7 <- predict(f, re_formula=NULL, summary=F)   # include all random effects
  f7[1:10,1:10] #columns are samples, rows predictions

  x <- pp_check(f , nsamples=1)
  head(x$data)

  data1 <- make_standata(formula = y ~ (1|country/site),
      family= bernoulli, data = d,)

  data1$Y
 
  ##########################################################################

  samples1 <- posterior_samples(fit, "^b")
  head(samples1)
  
  # extract posterior samples of group-level standard deviations
  samples2 <- posterior_samples(fit, "^sd_")
  head(samples2)

  samples3 <- posterior_samples(fit, "^r_country")
  head(samples3)[,1:10]  # show forst 10 columns

```

## Plot country SD estimates


```{r, echo=TRUE ,eval=TRUE} 
    
   # posterior samples
   mc.1 <- as.mcmc(f, pars = NA, exact_match = TRUE,
                   combine_chains = TRUE, inc_warmup = FALSE)   

   # get specific estimates 
   # names(mc.1[1,])
   mc_country <- mc.1[, grep("r_country[", names(mc.1[1,]), fixed=TRUE) ]
   # names(mc_country[1,])

   # convert to probabilities
   prob <- apply(mc_country,c(2),function(x) exp(x)/(1+exp(x))) 
   # function to calculate summary stats
   statz <- function(x) {
                   t(cbind(c(mean(x), quantile(x, c(0.025,0.975))) ))
           }

   #here are the country specific estimates  
   est <- apply(prob,2,statz)
 
  # forest plot see refernce
  label <- paste0("country", 1:25)
  mean  <-  est[1,]
  lower <-  est[2,]
  upper <-  est[3,]
  
  df <- data.frame(label, mean, lower, upper)
  
  # reverses the factor level ordering for labels after coord_flip()
  df$label <- factor(df$label, levels=rev(df$label))
  

  library(ggplot2)

  fp <- NULL
  fp <- ggplot(data=df, aes(x=label, y=mean, ymin=lower, ymax=upper)) +
          geom_pointrange() + 
          geom_hline(yintercept=sdcountry, lty=2) +  # add a dotted line at x=1 after flip
          coord_flip() +  # flip coordinates (puts labels on y axis)
          xlab("Label") + ylab("Mean (95% CI)") +
          theme_bw()  # use a white background
  print(fp)


```

## Plot site SD estimates

```{r, echo=TRUE ,eval=TRUE, fig.width=7, fig.height=12} 
    
   # posterior samples
   mc.1 <- as.mcmc(f, pars = NA, exact_match = TRUE,
                   combine_chains = TRUE, inc_warmup = FALSE)   

   # get specific estimates 
   # names(mc.1[1,])
   mc_country <- mc.1[, grep("r_country:", names(mc.1[1,]), fixed=TRUE) ]
   #names(mc_country[1,])

   # convert to probabilities
   prob <- apply(mc_country, c(2) ,function(x) exp(x)/(1+exp(x))) 

   # function to calculate summary stats
   statz <- function(x) {
                   t(cbind(c(mean(x), quantile(x, c(0.025,0.975))) ))
           }

   #here are the specific estimates  
   est <- apply(prob,2,statz)
 
  # forest plot see reference
  # label <- paste0("site", 1:dim(mc_country)[2])

  #get labbeling info

  x1 <- gsub("[^0-9\\_]", "",  names(mc_country[1,]))
  x2 <- gsub("\\_", "",  x1)

  x2a <- gsub("\\_", ".",  x1)
  co <- gsub(".*\\.(.*)\\..*", "\\1", x2a)

  site.only <- sub('.*\\.', '', x2a)
  label <-  as.numeric(site.only)
  mean  <-  est[1,]
  lower <-  est[2,]
  upper <-  est[3,]


  df <- data.frame(co, label, mean, lower, upper)
  df <- df[order(label),]

  # reverses the factor level ordering for labels after coord_flip()
  df$label <- factor(df$label, levels=rev(df$label))
  
  fp <- NULL
  fp <- ggplot(data=df, aes(x=label, y=mean, ymin=lower, ymax=upper, colour=co)) +
          geom_pointrange() + 
          geom_hline(yintercept=sdsite, lty=2) +  # add a dotted line at x=1 after flip
          coord_flip() +  # flip coordinates (puts labels on y axis)
          xlab("Label") + ylab("Mean (95% CI)") +
          theme_bw() + # use a white background +
    theme(legend.position="none") 

  print(fp)


```

## Comparing frequentist and Bayesian, what the difference between fitted and coef from model output?

```{r, eval=FALSE}

# fixef(fit, old=FALSE)
# object$fit@sim
# country predictions https://github.com/paul-buerkner/brms/issues/82

    #########################################
    f8 <- fitted(f, re_formula = ~ (1|country))   # is this the correct way for country level?
    ba <- unique(f8)[,1]    			                # Bayesian predictions
    ba[1:10]

    
    fr <- as.vector(unlist(1/(1+exp(-coef(fit0)$country))))  # freq blups
    plot(fr, ba); abline(0,1)				 # compare Bayesian and Frequentist
    
    #########################################
    # above differs to model coefficients?
    bc <- as.vector(coef(fit, old=TRUE)$country)
    bc <- 1/(1+exp(-bc))
    bc
    
    plot(fr, bc); abline(0,1)     # compare Bayesian and Frequentist
    
    #########################################
    f <-as.vector(unlist(coef(fit0)$country))  #frequentist
    b <- as.vector(coef(fit)$country[,1,])     #bayes
    plot(f, b); abline(0,1) 
    cor(f,b)

    
    f <- as.vector(unlist(coef(fit0)$site))  #frequentist
    # b <- as.vector(coef(fit)$`country:site`[,1,])     
    # bayes , needs ordering
    bc <- coef(fit, old=FALSE, summary=TRUE)$`country:site`
    df <- as.data.frame(bc)
    names(df) <- dimnames(bc)[[2]]
    df$sites <-     gsub(".*_", "", rownames(df))
    #df$countries <- gsub("_.*", "", rownames(df))
    df$sites <- as.numeric(as.character(df$sites))
    df <- df[order(df$sites),]
    b <- df[,1]
    plot(f, b); abline(0,1) 
    cor(f,b)

```

## Crude estimates

```{r, eval=TRUE}

foo <- d
 
library(dplyr)
foox <- foo %>% group_by(  country , site ) %>% summarise(N=length(y), ones=(mean(y))*length(y),
                                                          zero=(1-mean(y))*length(y),
                                                          mean=mean(y) ,                                                 )

foox <- data.frame(foox)
names(foox) <- c("Country","site","N","Yes","No","Mean")  

foox <- cbind(foox,binconf(foox$Yes, foox$N))
foox


foox1 <- foo %>% group_by(  country   ) %>% summarise(N=length(y), ones=(mean(y))*length(y),
                                                          zero=(1-mean(y))*length(y),
                                                          mean=mean(y) ,                                                 )

foox1 <- data.frame(foox1)
names(foox1) <- c("Country","N","Yes","No","Mean")  


```

## Plot crude estimates country level

```{r, eval=TRUE}


  foox1 <- cbind(foox1,binconf(foox1$Yes, foox1$N))
  est <- foox1

  label <- paste0("country", 1:25)
  mean  <-  est[,6]
  lower <-  est[,7]
  upper <-  est[,8]
  
  df <- data.frame(label, mean, lower, upper)
  
  # reverses the factor level ordering for labels after coord_flip()
  df$label <- factor(df$label, levels=rev(df$label))
  

  library(ggplot2)

  fp <- NULL
  fp <- ggplot(data=df, aes(x=label, y=mean, ymin=lower, ymax=upper, colour=label)) +
          geom_pointrange() + 
          geom_hline(yintercept=mu, lty=2) +  # add a dotted line at x=1 after flip
          coord_flip() +  # flip coordinates (puts labels on y axis)
          xlab("Label") + ylab("Mean (95% CI)") +
          theme_bw() +   # use a white background
          theme(legend.position="none") 
  print(fp)


```

## Plot crude site estimates

```{r, echo=TRUE ,eval=TRUE, fig.width=7, fig.height=12} 

  est <- foox
  label <-  est$site
  mean  <-  est[,6]
  lower <-  est[,8]
  upper <-  est[,9]


  df <- data.frame(co=foox$Country, label, mean, lower, upper)
  #df <- df[order(label),]

  # reverses the factor level ordering for labels after coord_flip()
  df$label <- factor(df$label, levels=rev(df$label))
  
  fp <- NULL
  fp <- ggplot(data=df, aes(x=label, y=mean, ymin=lower, ymax=upper, colour=co)) +
          geom_pointrange() + 
          geom_hline(yintercept=mu, lty=2) +  # add a dotted line at x=1 after flip
          coord_flip() +  # flip coordinates (puts labels on y axis)
          xlab("Label") + ylab("Mean (95% CI)") +
          theme_bw() + # use a white background +
    theme(legend.position="none") 

  print(fp)

# cat("\n")
# #cat("Summary Statistics")
# cat("\n")
# print(kable(foox, format="pandoc", digits=c(0,0,0,4),
#             caption = "crude estimates"))
# cat("\n")

```

## lmer estimates sites

```{r, eval=TRUE, fig.width=7, fig.height=12} 

  # manage the data
  # fco <- coef(fit0)$`site:country`
  # c(attr(ranef(fit0,condVar=TRUE)[[1]],"postVar"))  # co
  str(rr1 <- ranef(fit0, condVar = TRUE))
  # dotplot(rr1)                    ## default  # 
  # cV <- ranef(fit0, condVar = TRUE)   
  # # ranvar <- attr(cV[[1]], "postVar")
  # # sqrt(diag(ranvar[,,]))

  # get random effects from lmer and calculate confidence intervals too
  # http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#lme4
  # intercept
  fix <- fixef(fit0)              # intercept on log scale
  fix.var <- sqrt(diag(vcov(fit0)))   # intercept associated standard error^2
  # blups
  s.c <- rr1[1][1]                # site country random effects
  s.c.var <- c(attr(ranef(fit0,condVar=TRUE)[[1]],"postVar"))^0.5  # site country sds
  # make a datset
  vars <- as.data.frame(cbind(intercept=fix, intercept.var=fix.var , 
                              blup=as.vector(unlist(s.c)), blup.var=s.c.var ))
  # calculate CI for the random effects
  vars$est <- vars$intercept+vars$blup  # shift from intercept
  vars$lower <- vars$est+c(-1)* qnorm(0.975)*sqrt(vars$blup.var^2+vars$intercept.var^2)  #lower CI
  vars$upper <- vars$est+c( 1)* qnorm(0.975)*sqrt(vars$blup.var^2+vars$intercept.var^2)  #upper CI

  #log odds to probabilities
  A <- function(x) 1/(1+exp(-x))
  df <- vars
  df <- data.frame(df[,c(1:4)], apply(df[,c(5:7)],2, A) )
 

  label = rownames(s.c$`site:country`)
  df$sites <-     gsub(":.*","", label)
  df$countries <- gsub(".*:","", label)

  #plot
  est <- df
  label <-  est$sites
  mean  <-  est$est
  lower <-  est$lower
  upper <-  est$upper

  # intercept CI
  fit0fci <- confint(fit0)
  L <- fit0fci["(Intercept)",][1][[1]]
  U <- fit0fci["(Intercept)",][2][[1]]

  df <- data.frame(co=df$countries, label, mean, lower, upper)
  #df <- df[order(label),]

  # reverses the factor level ordering for labels after coord_flip()
  df$label <- factor(df$label, levels=rev(df$label))
  
  fp <- NULL
  fp <- ggplot(data=df, aes(x=label, y=mean, ymin=lower, ymax=upper, colour=co)) +
          geom_pointrange() + 
          geom_hline(yintercept=mu, lty=2) +  # add a dotted line at x=1 after flip
          geom_hline(yintercept= A(fix),  color="blue", linetype="dashed") +  # estimate
          geom_hline(yintercept=A(L),  color="blue", linetype="dashed") +   
          geom_hline(yintercept=A(U),  color="blue", linetype="dashed") +   
          coord_flip() +  # flip coordinates (puts labels on y axis)
          xlab("Label") + ylab("Mean (95% CI)") +
          theme_bw() + # use a white background +
    theme(legend.position="none") 

  print(fp)

```

## lmer estimates countries

```{r, eval=TRUE } 

 str(rr1 <- ranef(fit0, condVar = TRUE))
   

  # get random effects from lmer and calculate confidence intervals too
  # http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#lme4  
  # blups
  s.c <- rr1[2][1]                # country random effects
  s.c.var <- c(attr(ranef(fit0,condVar=TRUE)[[2]],"postVar"))^0.5  # country sds
  # make a datset
  vars <- as.data.frame(cbind(intercept=fix, intercept.var=fix.var , 
                              blup=as.vector(unlist(s.c)), blup.var=s.c.var ))
  # calculate CI for the random effects
  vars$est <- vars$intercept+vars$blup  # shift from intercept
  vars$lower <- vars$est+c(-1)* qnorm(0.975)*sqrt(vars$blup.var^2+vars$intercept.var^2)  #lower CI
  vars$upper <- vars$est+c( 1)* qnorm(0.975)*sqrt(vars$blup.var^2+vars$intercept.var^2)  #upper CI

  #log odds to probabilities
  A <- function(x) 1/(1+exp(-x))
  df <- vars
  df <- data.frame(df[,c(1:4)], apply(df[,c(5:7)],2, A) )
 

  label = rownames(s.c$`country`)
  df$countries <- gsub(".*:","", label)

  #plot
  est <- df
  label <-  est$countries
  mean  <-  est$est
  lower <-  est$lower
  upper <-  est$upper

  # intercept CI
# fit0fci <- confint(fit0)
#  L <- fit0fci["(Intercept)",][1][[1]]
#  U <- fit0fci["(Intercept)",][2][[1]]

  df <- data.frame( label, mean, lower, upper)
  #df <- df[order(label),]

  # reverses the factor level ordering for labels after coord_flip()
  df$label <- factor(df$label, levels=rev(df$label))
  
  fp <- NULL
  fp <- ggplot(data=df, aes(x=label, y=mean, ymin=lower, ymax=upper, colour=label)) +
          geom_pointrange() + 
          geom_hline(yintercept=mu, lty=2) +  # add a dotted line at x=1 after flip
          geom_hline(yintercept= A(fix),   color="blue", linetype="dashed") +  # estimate
          geom_hline(yintercept=A(L),   color="blue", linetype="dashed") +   
          geom_hline(yintercept=A(U),  color="blue", linetype="dashed") +   
          coord_flip() +  # flip coordinates (puts labels on y axis)
          xlab("Label") + ylab("Mean (95% CI)") +
          theme_bw() + # use a white background +
    theme(legend.position="none") 

  print(fp)














```

## REFERENCES

1 paper http://bmcmedresmethodol.biomedcentral.com/track/pdf/10.1186/1471-2288-11-94?site=bmcmedresmethodol.biomedcentral.com
1 code http://www.biomedcentral.com/content/supplementary/1471-2288-11-94-S1.PDF
1 code https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-11-94#MOESM1
2 forrest plot https://stackoverflow.com/questions/38062650/forest-plot-for-a-beginner-simple-example-using-ggplot2-edited
3 https://stackoverflow.com/questions/14639892/how-to-extract-words-between-two-period-using-rs-gsub
4 https://stackoverflow.com/questions/31774086/extracting-text-after-last-period-in-string-in-r
5 https://stats.stackexchange.com/questions/147836/prediction-interval-for-lmer-mixed-effects-model-in-r
6 http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#lme4

\clearpage

# COMPUTING ENVIRONMENT

```{r, echo=FALSE}

options(width=70)
opts_knit$set(root.dir = wd.code)   ##THIS SETS YOUR WORKING DIRECTORY
sessionInfo()
print(getwd())
stopTime<-proc.time()

```

This took `r (stopTime-startTime)[1][[1]]` seconds to execute.

```{r echo=FALSE}

# move stangle R file to a folder  
# put this at bottom & give it the same name as RMD file , replace any blanks with underscore
# https://amywhiteheadresearch.wordpress.com/2014/11/12/copying-files-with-r/
xxx <- "Simulate a binomial response and random effects.R"
rcode <-  gsub(' ','_', trimws(xxx))          # replace blank with underscore, this is needed
file.copy(rcode, getwd(),  overwrite=TRUE)# make a copy of the rcode in a folder of choice

```
 